\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-19 doc/USER_MANUAL/manual_SPECFEM3D.tex
updated both manuals

%Older versions of the code were initially developed by Dimitri Komatitsch at Institut de Physique du Globe (France)
%and then by Dimitri Komatitsch and Jeroen Tromp at Harvard University (USA).

Since then it has been developed and maintained by a development team: in alphabetical order,
Emanuele Casarotti,
Min Chen,
Vala Hj\"orleifsd\'ottir,
Emiljana Jorgji,
Jes\'us Labarta,
Sue Kientz,
Dimitri Komatitsch,
Qinya Liu,
Yang Luo,
Nicolas Le Goff,
Pieyre Le Loher,
Alessia Maggi,
Roland Martin,
Dennis McRitchie,
David Mich\'ea,
Daniel Peter,
Brian Savage,
Leif Strand,
Carl Tape,
Jeroen Tromp.\\

@@

%The main developers of the \texttt{SPECFEM3D} source code are Dimitri
%Komatitsch, Jeroen Tromp, and Qinya Liu. The following individuals
%(listed in alphabetical order) have also contributed to the development
%or improvement of the source code: Min Chen, Vala Hj\"orleifsd\'ottir,
%Jes\'us Labarta, and Leif Strand. The following individuals (listed in alphabetical
%order) contributed to this manual: Min Chen, Vala Hj\"orleifsd\'ottir,
%Sue Kientz, Dimitri Komatitsch, Qinya Liu, Alessia Maggi,
%Carl Tape, and Jeroen Tromp.

The manual's cover graphic was created
by Santiago Lombeyda from Caltech's Center for Advanced Computing Research (CACR) \url{http://www.cacr.caltech.edu}. \\

>>>>

Since then it has been developed and maintained by a development team: in alphabetical order,
Emanuele Casarotti,
Min Chen,
Vala Hj\"orleifsd\'ottir,
Emiljana Jorgji,
Jes\'us Labarta,
Dimitri Komatitsch,
Qinya Liu,
Yang Luo,
Nicolas Le Goff,
Pieyre Le Loher,
Alessia Maggi,
Roland Martin,
Dennis McRitchie,
David Mich\'ea,
Daniel Peter,
Brian Savage,
Leif Strand,
Carl Tape,
Jeroen Tromp.\\

@@

The manual's cover graphic was created
by Santiago Lombeyda from Caltech's Center for Advanced Computing Research (CACR) \url{http://www.cacr.caltech.edu}.
Sue Kientz assembled the manual.\\
